Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search

### 2021-06-22 docs/paper.tex
Reduced size of result plots to fit within margins
Optimized aspect ratio of plots

\documentclass[english,10pt]{article}
\usepackage{geometry}
\usepackage{inputenc}
\usepackage{csquotes}
\usepackage{hyperref}
\geometry{verbose,tmargin=3.5cm,bmargin=4cm,lmargin=3.8cm,rmargin=3.8cm}
\usepackage[backend=biber,style=ieee]{biblatex}
\addbibresource{sources.bib}
\makeatletter
\usepackage{url}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{wrapfig}
\usepackage{subcaption}
\makeatother
\usepackage{babel}
\usepackage{amsmath}
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}{Conjecture}
\newtheorem{property}{Property}
\newtheorem{corollary}{Corollary}[property] % Use theorem counter as `parent`
\usepackage{algorithm}
\newcommand{\Desc}[2]{\State \makebox[2em][l]{#1}#2}
\usepackage[noend]{algpseudocode}
\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother

@@

	To date, no research has been done on MAPFM. For MAPFM with a makespan objective instead of SIC, known as the combined target-assignment and pathfinding (TAPF) problem, there is the Conflict-Based Min-Cost-Flow (CBM) algorithm by Ma and Koenig \cite{ma2016} and a similar approach described in \cite{henkel2019}. Ma and Koenig's method builds upon the conflict-based search method and in particular on the Meta-Agent variation thereof also discussed in \cite{sharon2015} as a high-level search framework; in the low-level search, the connection between anonymous MAPF problems and max-flow problems (as discussed in \cite{yu2013}) is exploited to plan single teams in polynomial time.

@@

	\section{Experimental Results}
	\label{experiments}
	To compare the algorithms and variants described above with each other and with alternative MAPFM algorithms, two types of experiments were performed. In the first, ICTS-based algorithms discussed in this work are compared; in the second, the approximate ordered enumeration variant is compared to other algorithms for MAPFM \cite{donszelmann2021,baauw2021,jong2021,bruin2021}. This comparison data originates in \cite{donszelmann2021}. The values compared are the fraction of instances solved, and the average runtime per instance. It should be noticed that in the latter, the recorded runtimes converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work (Figure \ref{fig:i-times} and \ref{fig:r-times} for experiments 1 and 2), the fraction of instances solved is guiding in the analysis of results.
	\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
	\begin{figure*}[t]
		\centering
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1-p}
			\caption{25\% wall, 1 team}
			\label{fig:i-25-1-p}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3-p}
			\caption{25\% wall, 3 teams}
			\label{fig:i-25-3-p}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1-p}
			\caption{75\% wall, 1 team}
			\label{fig:i-75-1-p}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3-p}
			\caption{75\% wall, 3 teams}
			\label{fig:i-75-3-p}
		\end{subfigure}
		\caption{Fraction solved out of 50 maps by different ICTS-based algorithms}
		\label{fig:i-probs}
	\end{figure*}
	\begin{figure*}[b]
		\centering
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1-p}
			\caption{25\% wall, 1 team}
			\label{fig:r-25-1-p}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3-p}
			\caption{25\% wall, 3 teams}
			\label{fig:r-25-3-p}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1-p}
			\caption{75\% wall, 1 team}
			\label{fig:r-75-1-p}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3-p}
			\caption{75\% wall, 3 teams}
			\label{fig:r-75-3-p}
		\end{subfigure}
		\caption{Fraction solved out of 200 maps by MAPFM algorithms}
		\label{fig:r-probs}
	\end{figure*}

@@

	Future research could also look into improving the ICTS-m method described using for instance more extensive pruning or properties of the problem such as lower-bounds on per-team solution SIC that can be computed using the Hungarian Algorithm. Another approach to explore would be hybridized approaches that enumerate partially constrained MAPFM instances which can be solved using any MAPFM solver. In this way, the benefit of the successive bounding of the search could be exploited and by carefully picking which agents to constrain, these constrained MAPFM instances could potentially be made relatively easy.

@@

	\printbibliography
	\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
	\begin{figure*}[t]
		\centering
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1}
			\caption{25\% wall, 1 team}
			\label{fig:i-25-1}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3}
			\caption{25\% wall, 3 teams}
			\label{fig:i-25-3}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1}
			\caption{75\% wall, 1 team}
			\label{fig:i-75-1}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3}
			\caption{75\% wall, 3 teams}
			\label{fig:i-75-3}
		\end{subfigure}
		\caption{Average solving time of different ICTS-based algorithms with a timeout of 120s}
		\label{fig:i-times}
	\end{figure*}
	\begin{figure*}[b]
		\centering
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1}
			\caption{25\% wall, 1 team}
			\label{fig:r-25-1}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3}
			\caption{25\% wall, 3 teams}
			\label{fig:r-25-3}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1}
			\caption{75\% wall, 1 team}
			\label{fig:r-75-1}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3}
			\caption{75\% wall, 3 teams}
			\label{fig:r-75-3}
		\end{subfigure}
		\caption{Average solving time of MAPFM algorithms with a timeout of 120s}
		\label{fig:r-times}
	\end{figure*}

>>>>

\documentclass[english]{article}
\usepackage{geometry}
\usepackage{inputenc}
\usepackage{csquotes}
\usepackage{hyperref}
\geometry{verbose,tmargin=3.5cm,bmargin=4cm,lmargin=3.8cm,rmargin=3.8cm}
\newcommand\graphwidth{0.49\textwidth}
\usepackage[backend=biber,style=ieee]{biblatex}
\addbibresource{sources.bib}
\makeatletter
\usepackage{url}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{wrapfig}
\usepackage{subcaption}
\makeatother
\usepackage{babel}
\usepackage{amsmath}
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}{Conjecture}
\newtheorem{property}{Property}
\newtheorem{corollary}{Corollary}[property] % Use theorem counter as `parent`
\usepackage{algorithm}
\newcommand{\Desc}[2]{\State \makebox[2em][l]{#1}#2}
\usepackage[noend]{algpseudocode}
\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother

@@

	Little to no research has been done on MAPFM and solving it optimally. For MAPFM with a makespan objective instead of SIC, known as the combined target-assignment and pathfinding (TAPF) problem, there is the Conflict-Based Min-Cost-Flow (CBM) algorithm by Ma and Koenig \cite{ma2016} and a similar approach described in \cite{henkel2019}. Ma and Koenig's method builds upon the conflict-based search method and in particular on the Meta-Agent variation thereof also discussed in \cite{sharon2015} as a high-level search framework; in the low-level search, the connection between anonymous MAPF problems and max-flow problems (as discussed in \cite{yu2013}) is exploited to plan single teams in polynomial time.

@@

	\section{Experimental Results}
	\label{experiments}
	To compare the algorithms and variants described above with each other and with alternative MAPFM algorithms, two types of experiments were performed. In the first, ICTS-based algorithms discussed in this work are compared; in the second, the approximate ordered enumeration variant is compared to other algorithms for MAPFM \cite{donszelmann2021,baauw2021,jong2021,bruin2021}. This comparison data originates in \cite{donszelmann2021}. The values compared are the fraction of instances solved, and the average runtime per instance. It should be noticed that in the latter, the recorded runtimes converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work (Figure \ref{fig:i-times} and \ref{fig:r-times} for experiments 1 and 2), the fraction of instances solved is guiding in the analysis of results.
	%\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
	\begin{figure*}[t]
		\centering
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1-p}
			\caption{25\% wall, 1 team}
			\label{fig:i-25-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3-p}
			\caption{25\% wall, 3 teams}
			\label{fig:i-25-3-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1-p}
			\caption{75\% wall, 1 team}
			\label{fig:i-75-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3-p}
			\caption{75\% wall, 3 teams}
			\label{fig:i-75-3-p}
		\end{subfigure}
		\caption{Fraction solved out of 50 maps by different ICTS-based algorithms}
		\label{fig:i-probs}
	\end{figure*}
	\begin{figure*}[b]
		\centering
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1-p}
			\caption{25\% wall, 1 team}
			\label{fig:r-25-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3-p}
			\caption{25\% wall, 3 teams}
			\label{fig:r-25-3-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1-p}
			\caption{75\% wall, 1 team}
			\label{fig:r-75-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3-p}
			\caption{75\% wall, 3 teams}
			\label{fig:r-75-3-p}
		\end{subfigure}
		\caption{Fraction solved out of 200 maps by MAPFM algorithms}
		\label{fig:r-probs}
	\end{figure*}

@@

	Future research could also look into improving the ICTS-m method described using for instance more extensive pruning or properties of the problem such as lower-bounds on per-team solution SIC that can be computed using the Hungarian Algorithm. Another approach to explore would be hybridized approaches that enumerate partially constrained MAPFM instances which can be solved using any MAPFM solver. In this way, the benefit of the successive bounding of the search could be exploited and by carefully selecting agents to constrain, these constrained MAPFM instances could potentially be made relatively easy.

@@

	\printbibliography
	\newpage
	\begin{figure*}[t]
		\centering
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1}
			\caption{25\% wall, 1 team}
			\label{fig:i-25-1}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3}
			\caption{25\% wall, 3 teams}
			\label{fig:i-25-3}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1}
			\caption{75\% wall, 1 team}
			\label{fig:i-75-1}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3}
			\caption{75\% wall, 3 teams}
			\label{fig:i-75-3}
		\end{subfigure}
		\caption{Average solving time of different ICTS-based algorithms with a timeout of 120s}
		\label{fig:i-times}
	\end{figure*}
	\begin{figure*}[b]
		\centering
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1}
			\caption{25\% wall, 1 team}
			\label{fig:r-25-1}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3}
			\caption{25\% wall, 3 teams}
			\label{fig:r-25-3}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1}
			\caption{75\% wall, 1 team}
			\label{fig:r-75-1}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3}
			\caption{75\% wall, 3 teams}
			\label{fig:r-75-3}
		\end{subfigure}
		\caption{Average solving time of MAPFM algorithms with a timeout of 120s}
		\label{fig:r-times}
	\end{figure*}
